abxD01 Paper

### 2015-03-02 PAPER.Rmd
Fix issue with block code

> ### CFU stats comparison
> To compare CFU levels: 
```{r, eval=TRUE}

@@

```
> 
> ### Amova to compare resulting community structures
> Amova calculation in mothur to determine the uniqueness of each community structure:
> 
```
dist.shared(shared=abxD01.final.an.unique_list.0.03.topdose2.shared, calc=thetayc-jclass, subsample=1625)
amova(phylip=abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.dist, design=topdose_design_byABX.txt, iters=1000000)

```
> This results in the file called "abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.amova" located in the github folder. The results of these are summarized in "amova8expgroups.xlsx".
> 
> ### Figure 1: Bargraph
> 
> This figure was built using the R script called "stacked.barcharts.r", which contains the stackedbarcharts() funciton in the abxD01 folder.The input files are listed in Github. The graph can be sorted 2 ways either by the untreated's decreasing relabund (sortbyphyl=FALSE), or by the most abundant within each phylum (sortbyphyl=TRUE). For each treatment, the resulting *C. difficile* CFU/g Feces is also labeled on the Y axis below the treatment name. 
> The parameters I changed in the r script were:
```{r, eval=FALSE}
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")
library(plotrix)
# Generate the 
stackedbarcharts(file="~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.2.subsample.relabund.topdose2.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 1/topdose_tx2_barchart_ids.csv", graphLabels = abx, sortbyphyl = TRUE, graphbyphyl = FALSE)

@@

```
> 
> Files saved as "topdose2_tx1_sorted_10x20.pdf" and "topdose2_tx2_sorted_10x20.pdf".
> 
> ### Supplemental Figure 1: correlation plot of diversity with *C. difficile*
> 
> For the correlation calculations see the next section of the results.
> Figure making:
> 
--------

>>>>

> ### CFU stats comparison
> To compare CFU levels:

@@

> ### Amova to compare resulting community structures
> Amova calculation in mothur to determine the uniqueness of each community structure:
>

```
dist.shared(shared=abxD01.final.an.unique_list.0.03.topdose2.shared, calc=thetayc-jclass, subsample=1625)
amova(phylip=abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.dist, design=topdose_design_byABX.txt, iters=1000000)

```
> This results in the file called "abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.amova" located in the github folder. The results of these are summarized in "amova8expgroups.xlsx".
> 
> ### Figure 1: Bargraph
> 
> This figure was built using the R script called "stacked.barcharts.r", which contains the stackedbarcharts() funciton in the abxD01 folder.The input files are listed in Github. The graph can be sorted 2 ways either by the untreated's decreasing relabund (sortbyphyl=FALSE), or by the most abundant within each phylum (sortbyphyl=TRUE). For each treatment, the resulting *C. difficile* CFU/g Feces is also labeled on the Y axis below the treatment name. 
> The parameters I changed in the r script were:

```{r, eval=FALSE}
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")
library(plotrix)
# Generate the 
stackedbarcharts(file="~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.2.subsample.relabund.topdose2.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 1/topdose_tx2_barchart_ids.csv", graphLabels = abx, sortbyphyl = TRUE, graphbyphyl = FALSE)

@@

> Files saved as "topdose2_tx1_sorted_10x20.pdf" and "topdose2_tx2_sorted_10x20.pdf".
> 
> ### Supplemental Figure 1: correlation plot of diversity with *C. difficile*
> 
> For the correlation calculations see the next section of the results.
> Figure making:
>
